% ATS-compliant resume for Ruchira Dhar
% Compile with: pdflatex RuchiraResume.tex
\documentclass[11pt,letterpaper]{article}

\usepackage[top=0.75in, bottom=0.75in, left=0.9in, right=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

% Section formatting — bold, full-width rule underneath
\titleformat{\section}
  {\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=3pt, parsep=0pt}
\pagestyle{empty}

% Helper: right-aligned date on the same line as a bold title
\newcommand{\entry}[2]{%
  \noindent\textbf{#1}\hfill\textit{#2}\\[-2pt]%
}

\begin{document}

% ------------------------------------------------------------------ HEADER --
\begin{center}
  {\LARGE\bfseries Ruchira Dhar}\\[6pt]
  %Copenhagen, Denmark
  \enspace$\cdot$\enspace \href{mailto:rudh@di.ku.dk}{Email: rudh@di.ku.dk}
  \enspace$\cdot$\enspace \\
    \href{https://ruchiradhar.github.io}{Website}
  \enspace$\cdot$\enspace
    \href{https://linkedin.com/in/ruchira-dhar-105427122}{LinkedIn}
  \enspace$\cdot$\enspace
    \href{https://scholar.google.com/citations?user=YgAMn9gAAAAJ}{Google Scholar}
\end{center}

% --------------------------------------------------------------- EDUCATION --
\section{Education}

\entry{PhD in Computer Science}{2023 -- Present}
University of Copenhagen \hfill Copenhagen, Denmark\\
Supervisor: Dr.\ Anders S\o{}gaard (PhD, University of Copenhagen)\\
\textit{Research Focus}: AI Evaluation, Efficient Evaluation, LLM

\medskip

\entry{Masters in Linguistics}{2018--2020}
English and Foreign Languages University \hfill Hyderabad, India\\
Supervisor: Dr.\ Utpal Lahiri (PhD, MIT)\\
\textit{Course}: Natural Language Processing, Artificial Neural Networks, Mathematical Linguistics

% --------------------------------------------------------------- EXPERIENCE --
\section{Experience}

\entry{AI Scientist,  Flowrite Oy (Helsinki, Finland)}{02/2022 -- 06/2023}
\textit{Early-stage startup in productivity enhancement with Generative AI}
\begin{itemize}
  \item Building model evaluation pipelines for generative LLMs
  \item Developed large-scale annotation and user feedback frameworks for model alignment
\end{itemize}

\medskip
\entry{NLG Engineer, Cerence Inc (Pune, India)}{05/2021 -- 02/2022}
\textit{Enterprise language \& speech technology for the automotive industry}
\begin{itemize}
  \item Engineered NLG and Speech Recognition for multilingual voice assistants across 10+ languages
  \item Conducted evaluation for speech-driven interactions in real-world automotive settings
\end{itemize}

\medskip
\entry{Associate Engineer, Kore AI (Hyderabad, India)}{01/2021 -- 05/2021}
\textit{Enterprise conversational AI solutions}
\begin{itemize}
  \item Developed production-ready chatbot solutions leveraging intent classification and entity recognition
  \item Collaborated with cross-functional teams to deliver AI-powered tools for customer engagement
\end{itemize}

\medskip
\entry{Research Fellow, Indian Institute of Technology (IIT) (Delhi, India)}{09/2020 -- 12/2020}
Delhi, India
\begin{itemize}
  \item Advanced research on multilingual semantic annotation pipelines in NLP
\end{itemize}


% ------------------------------------------------------------ AFFILIATIONS --
\section{Affiliations}

\entry{Visiting Researcher, LRE Lab, ETH Zurich}{2026 -- Present}
Researching low-cost efficient evaluation methods for LLMs.



\medskip
\entry{Venture Fellow, Creator Fund}{2025 -- Present}
Evaluating product and infrastructure for AI startups for technical diligence.

\medskip
\entry{Open Science Lead, Cohere Labs}{2024 -- Present}
Driving AI research engagement across a global community of 200+ researchers.

\medskip
\entry{Fellow, Centre for Philosophy of AI, University of Copenhagen}{2023 -- Present}
Leading research on the socio-ethical implications of AI systems and AI governance.


% ------------------------------------------------------ FIRST-AUTHOR PUBS --
\section{First-Author Publications}

\begin{itemize}

  \item \textbf{Ruchira Dhar}, Qiwei Peng, Anders S\o{}gaard.
    ``Evaluating Adjective-Noun Compositionality in LLMs: Functional vs
    Representational Perspectives.''
    \textit{The 15th Joint Conference on Lexical and Computational Semantics
    (*SEM), ACL}, 2026. \url{https://arxiv.org/abs/2603.09994}

  \item \textbf{Ruchira Dhar}, Stephanie Brandl, Ninell Oldenburg,
    Anders S\o{}gaard.
    ``Beyond Technocratic XAI: The Who, What \& How in Explanation Design.''
    \textit{AAAI/ACM Conference on AI, Ethics, \& Society (AIES)}, 2025. \url{https://ojs.aaai.org/index.php/AIES/article/view/36586}

\end{itemize}

% ---------------------------------------- FIRST-AUTHOR WORKSHOP / PREPRINT --
\section{First Author Workshop Papers \& Preprints}

\begin{itemize}

  \item \textbf{Ruchira Dhar}, Anders S\o{}gaard.
    ``Evaluation Revisited: A Taxonomy of Evaluation Concerns in Natural
    Language Processing.''
    \textit{Preprint}, 2026.\\
    \url{https://arxiv.org/abs/2604.25923}

  \item \textbf{Ruchira Dhar}, Ninell Oldenburg, Anders S\o{}gaard.
    ``On the Measure of a Model: From Intelligence to Generality.''
    \textit{Science of Benchmarking and Evaluating AI Workshop, EurIPS}, 2025.\\
    \url{https://arxiv.org/abs/2511.11773}

  \item \textbf{Ruchira Dhar}, Danae Sanchez Villegas, Antonia Karamolegkou,
    Alice Schiavone, Yifei Yuan, Xinyi Chen, Jiaang Li, Stella Frank,
    Laura De Grazia, Monorama Swain, Stephanie Brandl, Daniel Hershcovich,
    Anders S\o{}gaard, Desmond Elliott.
    ``EvalCards: A Framework for Standardized Evaluation Reporting.''
    \textit{Science of Benchmarking and Evaluating AI Workshop, EurIPS}, 2025.\\
    \url{https://arxiv.org/abs/2511.21695}

  \item \textbf{Ruchira Dhar}, Anders S\o{}gaard.
    ``From Words to Worlds: Compositionality for Cognitive Architectures.''
    \textit{LLMs \& Cognition Workshop, ICML}, 2024.\\
    \url{https://openreview.net/forum?id=2eA9b52PAW}

\end{itemize}

% ----------------------------------------------------------- INVITED TALKS --
\section{Invited Talks}

\begin{itemize}

  \item ``Are We Testing the Right Things in Multi-Agent AI?''\\
    UKAI Forum \& Meridian Cambridge, St John's College,
    Cambridge, United Kingdom. October 2025.

  \item ``The Completeness Problem: Beyond Human Metrics in Assessing
    Abilities of Cognitive Systems.''\\
    International Symposium on AI \& Neuroscience (ACAIN),
    Italy. September 2024.

\end{itemize}

% --------------------------------------------------------------- TEACHING --
\section{Teaching}

\entry{Teaching Assistant --- NLP Course (NDAK18000U)}{2023 -- Present}
Department of Computer Science, University of Copenhagen\\
Undergraduate and graduate-level instruction in natural language processing.

% ------------------------------------------------------- SKILLS --
\section{Skills}

\noindent
\textbf{Research:}
  Natural Language Processing, Large Language Model, AI Benchmarking,
  Multi-Agent Systems, Responsible AI, AI Governance, Cognitive Science,
  Explainable AI (XAI), Linguistics\\[3pt]
\textbf{Software:}
  Python, PyTorch, HuggingFace Transformers, Scikit-Learn, NumPy, Pandas,
  SpaCy, NLTK, Jupyter, Git, LaTeX.\\[3pt]
\textbf{Languages:}
Danish (Limited Working Proficiency),
English (Native Proficiency), 
Bengali (Native Proficiency),
Hindi (Native Proficiency)

\end{document}
